Placeholder

### 2021-02-09 Paper_Histograms.Rmd
Added gridExtra package to library

# Read in data
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(multipanelfigure)

@@

gridExtra::grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)

>>>>

# Read in data
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)

@@

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)
